Gammapy: A Python package for gamma-ray astronomy

### 2022-08-08 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno KHÉLIFI <khelifi@in2p3.fr>

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.

>>>>

Because the background models suffer from strong uncertainties it is required
to correct them from the data themselves. Several techniques are commonly used
in TeV \gammaray astronomy such as field-of-view background normalization or
background measurement in reflected regions, see~\cite{Berge07}.
Specific \code{Makers} such as the \code{FoVBackgroundMaker} or the
\code{ReflectedRegionsBackgroundMaker} are in charge of this step.
